Finding the True MVP

### 2024-12-12 paper/paper.qmd
Edits to Tables

-   `Team:` Whether the player was in the 1st, 2nd, or 3rd All NBA Teams or OVR if they did not make the top three teams but still received a vote.
-   `Pos:` The player's position including the generalized positions G, F, C, for Guard, Forward, and Center respectively.
-   `Player:` The name of the NBA player.
-   `Age:` The age of the NBA player.
-   `Tm:` The three letter designation for the NBA team the player played for the year.
-   `G:` Games played by the player.
-   `MP:` Minutes played per game.
-   `PTS:` Points per game.
-   `TRB:` Total Rebounds per game, including offensive and defensive rebounds.
-   `BLK:` Blocks per game
-   `STL:` Steals Per game
-   `WS:` The amount of wins allocated to the individual player

@@

-   `Player:` The name of the NBA player.
-   `Year:` The year in which the player was selected as MVP.
-   `Tm:` The three letter designation for the NBA team the player played for the year.
-   `G:` Games played by the player.
-   `MP:` Minutes played per game.
-   `PTS:` Points per game.
-   `TRB:` Total Rebounds per game, including offensive and defensive rebounds.
-   `BLK:` Blocks per game
-   `STL:` Steals Per game
-   `WS:` The amount of wins allocated to the individual player

@@

We expect a positive relationship between MVP Index and points, assists, rebounds, blocks, steals, and win shares, as these variables collectively define the MVP Index. Additionally, we anticipate a positive relationship because all these statistics indicate strong player performance. The larger any one of these statistics is, the larger the MVP Index will be for the respective player. However, a player who does not acquire many blocks or assists will not necessarily have a low MVP rating; they will simply need to compensate with higher performance in other areas. As shown in @sec-model-details, the model has a p-value of less than $2.2 \times 10^{-16}$, which is very low and gives us confidence that the model is accurate.

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| label: tbl-modelresults
#| fig-cap: "Historical MVP and Player with highest MVP Index since 2014"

@@

@@

print(combined_table)
print(tiny_combined_table)

@@

@@

print(mvp_table)
```

@@

@@

print(Real_MVP_Datas)
```

@@

```{r}
#| include: true
#| warning: false
#| message: false
#| echo: false
lm_summary <- summary(lm_model)

>>>>

-   `Team:` Whether the player was in the 1st, 2nd, or 3rd All NBA Teams or OVR if they did not make the top three teams but still received a vote.
-   `Pos:` The player's position including the generalized positions G, F, C, for Guard, Forward, and Center respectively
-   `Player:` The name of the NBA player
-   `Age:` The age of the NBA player
-   `Tm:` The three letter designation for the NBA team the player played for the year
-   `G:` Games played by the player
-   `MP:` Minutes played per game
-   `PTS:` Points per game
-   `TRB:` Total Rebounds per game, including offensive and defensive rebounds
-   `AST:` Assists Per game
-   `BLK:` Blocks per game
-   `STL:` Steals Per game
-   `WS:` The amount of wins allocated to the individual player

@@

-   `Player:` The name of the NBA player.
-   `Year:` The year in which the player was selected as MVP
-   `Tm:` The three letter designation for the NBA team the player played for the year
-   `G:` Games played by the player
-   `MP:` Minutes played per game
-   `PTS:` Points per game
-   `AST:` Assists Per game
-   `TRB:` Total Rebounds per game, including offensive and defensive rebounds
-   `BLK:` Blocks per game
-   `STL:` Steals Per game
-   `WS:` The amount of wins allocated to the individual player

@@

We expect a positive relationship between MVP Index and points, assists, rebounds, blocks, steals, and win shares, as these variables collectively define the MVP Index. Additionally, we anticipate a positive relationship because all these statistics indicate strong player performance. The larger any one of these statistics is, the larger the MVP Index will be for the respective player. However, a player who does not acquire many blocks or assists will not necessarily have a low MVP rating; they will simply need to compensate with higher performance in other areas. As shown in @sec-model-details, the model has a p-value of less than $2.2 \times 10^{-16}$, which is very low and gives us confidence that the model is accurate, as well as an $R^{2}$ of $R^{2} = 0.8992$, with a corresponding $R = 0.9483$.

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| label: tbl-modelresults

@@

combined_table <- combined_table %>%
  rename(
    `Year` = Year,
    `Sim Player` = `Simulated Data - Player`,
    `Sim MVP` = `Simulated Data - MVP Index`,
    `Hist Player` = `Historical Data - Player`,
    `Hist MVP` = `Historical Data - MVP Index`
  )

@@

@@

```{r}
#| echo: false

print(tiny_combined_table)
```

@@

mvp_table <- mvp_table %>% select(-Source)

tiny_mvp_table <- tt(mvp_table)

print(tiny_mvp_table)
```

@@

Real_MVP_Data_f <- Real_MVP_Datas %>% select(-FG., -X3P., -FT., -WS.48, -Voting, -Lg, -Tm, -G, -MP)

@@

tiny_real_mvp <- tt(Real_MVP_Data_f)
print(tiny_real_mvp)
```

@@

```{r}
#| include: true
#| warning: false
#| message: false
#| echo: false
#| 
lm_summary <- summary(lm_model)
